VariantSpark: Population Scale Clustering of Genotype Information

### 2015-09-22 doc/publications/journal2014/paper.tex
couple of changes

\subsection*{Graph visualisation}
\variantSpark{} supports visualisation of the resulting population clusters by generating a file that can be loaded into {\sc Gephi}~\cite{ICWSM09154}.
Figure 3 visualises the clusters generated by \variantSpark{} from the 1000 Genomes Project data. 
As discussed in the previous section, three of the four clusters (super-populations AFR, EAS and AMR) are relatively-homogeneous; the fourth is more mixed and 
consists predominantly of individuals labelled EUR and AMR providing a visual representation of the ARI of 0.84.

>>>>

\subsection*{Graph visualisation}
\variantSpark{} supports visualisation of the resulting population clusters by generating a file that can be loaded into {\sc Gephi}~\cite{ICWSM09154}.
Figure 3 visualises the clusters generated by \variantSpark{} from the 1000 Genomes Project data. 
As discussed in the previous section, three of the four clusters (super-populations AFR, EAS and AMR) are relatively homogeneous; the fourth is more mixed and 
consists predominantly of individuals labelled EUR and AMR providing a visual representation of the ARI of 0.84.
